---
title: "Trends Analysis"
author: "Campbell Miller"
date: "2022-11-03"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pacman::p_load(ggplot2, here, dplyr, readr, readxl, tidyverse, broom, scales, gsubfn, stringr, ggthemes, viridis)

data <- read.csv('CaseStudy.csv')
```

```{r}
glimpse(data)

dim(data)
str(data)


unique(data$Date.of.Service)
unique(data$Month.of.Service)
unique(data$Quarter.of.Service)
unique(data$Payment.Amount )
unique(data$Payer)
unique(data$Provider.Name)
unique(data$Service.Type )
unique(data$Service.Subtype)
unique(data$Clinic.Location)
unique(data$CPT)
unique(data$Patient.Diagnosis)
unique(data$New.Patient.Indicator)
unique(data$Referral.Source)
```

```{r}
#data1 is only chemo infusion for provider 1
data1 <- data
data1 <- filter(data1, Service.Subtype == "Chemotherapy Infusion")
data1 <- filter(data1, Provider.Name == "Provider 1")

data1 <- data1 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data1$Quarter.of.Service <- factor(data1$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data1$Quarter.of.Service)
```


```{r}
#data2 is only chemo infusion for Provider 2
data2 <- data
data2 <- filter(data2, Service.Subtype == "Chemotherapy Infusion") #| Service.Subtype == "Non-Chemotherapy Infusion")
data2 <- filter(data2, Provider.Name == "Provider 2")

data2 <- data2 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))
#this code reorganizes the dates 
data2$Quarter.of.Service <- factor(data2$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
table(data2$Quarter.of.Service)

#this code is used to make a nonchemo data set for provider 2
data22 <- data
data22 <- filter(data22, Service.Subtype == "Non-Chemotherapy Infusion")
data22 <- filter(data22, Provider.Name == "Provider 2")

data22 <- data22 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                         ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))
data22$Quarter.of.Service <- factor(data22$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

#chemo graph
ggplot(data2, aes(x = Quarter.of.Service, y = Quarter.of.Service1)) + 
  geom_bar(stat = "identity")
#non chemo graph
ggplot(data22, aes(x = Quarter.of.Service, y = Quarter.of.Service1)) + 
  geom_bar(stat = "identity") 

#sums <- data2 %>%
 # group_by(Quarter.of.Service) %>%
  #summarize(Total = sum(Quarter.of.Service1))

```

```{r}
data3 <- data
data3 <- filter(data3, Service.Subtype == "Chemotherapy Infusion")
data3 <- filter(data3, Provider.Name == "Provider 3")

data3 <- data3 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data3$Quarter.of.Service <- factor(data3$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data3$Quarter.of.Service)
```

```{r}
data4 <- data
data4 <- filter(data4, Service.Subtype == "Chemotherapy Infusion")
data4 <- filter(data4, Provider.Name == "Provider 4")

data4 <- data4 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data4$Quarter.of.Service <- factor(data4$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data4$Quarter.of.Service)
```

```{r}
data5 <- data
data5 <- filter(data5, Service.Subtype == "Chemotherapy Infusion")
data5 <- filter(data5, Provider.Name == "Provider 5")

data5 <- data5 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data5$Quarter.of.Service <- factor(data5$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data5$Quarter.of.Service)
```

```{r}
data6 <- data
data6 <- filter(data6, Service.Subtype == "Chemotherapy Infusion")
data6 <- filter(data6, Provider.Name == "Provider 6")

data6 <- data6 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data6$Quarter.of.Service <- factor(data6$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data6$Quarter.of.Service)
```

```{r}
data7 <- data
data7 <- filter(data7, Service.Subtype == "Chemotherapy Infusion")
data7 <- filter(data7, Provider.Name == "Provider 7")

data7 <- data7 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data7$Quarter.of.Service <- factor(data7$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data7$Quarter.of.Service)
```

```{r}
data8 <- data
data8 <- filter(data8, Service.Subtype == "Chemotherapy Infusion")
data8 <- filter(data8, Provider.Name == "Provider 8")

data8 <- data8 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))

data8$Quarter.of.Service <- factor(data8$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(data8$Quarter.of.Service)
```



```{r}
table(data1$Quarter.of.Service)
table(data2$Quarter.of.Service)
table(data3$Quarter.of.Service)
table(data4$Quarter.of.Service)
table(data5$Quarter.of.Service)
table(data6$Quarter.of.Service)
table(data7$Quarter.of.Service)
table(data8$Quarter.of.Service)
```




```{r}
#total drug admin per oncologist making datafarmes for each
totaldrug1 <- data
totaldrug1 <- filter(totaldrug1, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug1 <- filter(totaldrug1, Provider.Name == "Provider 1") 

totaldrug2 <- data
totaldrug2 <- filter(totaldrug2, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug2 <- filter(totaldrug2, Provider.Name == "Provider 2") 

totaldrug3 <- data
totaldrug3 <- filter(totaldrug3, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug3 <- filter(totaldrug3, Provider.Name == "Provider 3") 

totaldrug4 <- data
totaldrug4 <- filter(totaldrug4, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug4 <- filter(totaldrug4, Provider.Name == "Provider 4") 

totaldrug5 <- data
totaldrug5 <- filter(totaldrug5, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug5 <- filter(totaldrug5, Provider.Name == "Provider 5") 

totaldrug6 <- data
totaldrug6 <- filter(totaldrug6, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug6 <- filter(totaldrug6, Provider.Name == "Provider 6") 

totaldrug7 <- data
totaldrug7 <- filter(totaldrug7, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug7 <- filter(totaldrug7, Provider.Name == "Provider 7") 

totaldrug8 <- data
totaldrug8 <- filter(totaldrug8, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")
totaldrug8 <- filter(totaldrug8, Provider.Name == "Provider 8") 



table(totaldrug1$Service.Subtype)
table(totaldrug2$Service.Subtype)
table(totaldrug3$Service.Subtype)
table(totaldrug4$Service.Subtype)
table(totaldrug5$Service.Subtype)
table(totaldrug6$Service.Subtype)
table(totaldrug7$Service.Subtype)
table(totaldrug8$Service.Subtype)
```

```{r}
drug <- data
drug <- filter(drug, Service.Subtype == "Chemotherapy Infusion" | Service.Subtype == "Non-Chemotherapy Infusion")

drug <- drug %>%
   mutate(Provider.Name1 = ifelse(Provider.Name == "Provider 1", 1,
                                            ifelse(Provider.Name == "Provider 2", 1,
                                                   ifelse(Provider.Name == "Provider 3", 1,
                                                          ifelse(Provider.Name == "Provider 4", 1, 
                                                                 ifelse(Provider.Name == "Provider 5", 1,
                                                                   ifelse(Provider.Name == "Provider 6", 1,
                                                                    ifelse(Provider.Name == "Provider 7", 1,
                                                                       ifelse(Provider.Name == "Provider 8", 1, 0)))))))))
#graph showing total drug admins per provider based on chemo and non chemo
ggplot(drug, aes(x = Provider.Name, y = Provider.Name1, fill = factor(Service.Subtype, levels=c("Non-Chemotherapy Infusion", "Chemotherapy Infusion")))) +
  geom_bar(stat = 'identity') +
  xlab("") +
  ylab("Drug Administrations") +
  ggtitle("Total Drug Administations over 4 Quarters by Provider") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata() +
  scale_fill_manual(values = color1, name = "") +
  labs(fill = "Service.Subtype")


#vector for colors you want in the graph
color1 = c('indianred3', 'cornflowerblue')

table(drug$Provider.Name)

drug1 <- drug %>%
     mutate(Provider.Name1 = ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "4/1/2021", 331,
                             ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "7/1/2021", 335,
                             ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "10/1/2021", 389,
                             ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "1/1/2022", 443,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "4/1/2021", 385,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "7/1/2021", 390,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "10/1/2021", 377,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "1/1/2022", 548,                   
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "4/1/2021", 626,
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "7/1/2021", 408,
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "10/1/2021", 433,
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "1/1/2022", 407,      
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "4/1/2021", 362,
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "7/1/2021", 318,
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "10/1/2021", 220,
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "1/1/2022", 270,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "4/1/2021", 226,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "7/1/2021", 215,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "10/1/2021", 472,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "1/1/2022", 507,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "4/1/2021", 447,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "7/1/2021", 369,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "10/1/2021", 274,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "1/1/2022", 0,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "4/1/2021", 521,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "7/1/2021", 529,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "10/1/2021", 78,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "1/1/2022", 0,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "4/1/2021", 239,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "7/1/2021", 282,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "10/1/2021", 213,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "1/1/2022", 180, 0)))))))))))))))))))))))))))))))))
                                     
                                     
drug1$Quarter.of.Service <- factor(drug1$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))                                     
                                     
                                  
#graph showing the change in chemo drug admins per provider through the quarters
ggplot(drug1, aes(x = Quarter.of.Service, y = Provider.Name1, color = Provider.Name, group = Provider.Name)) +
  geom_point() +
  geom_line() +
  xlab("Quarter of Service") +
  ylab("Chemo Drug Infusions") +
  ggtitle("Chemo Drug Administrations by Provider over 4 Quarters") +
  scale_color_brewer(palette = "Dark2", name = "") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()
  


```


##KPI'S

//TOTAL DROG ADMINISTRATIONS

1. total drug administrations

2. chemo vs non chemo administrations 

Both 1 and 2 done by graph above

Target: 400 chemo drug administrations per quarter per medical oncologist

Provider 1 (new provider) 1/4 chemo kpi
  Quarter1 331
  Quarter2 335
  Quarter3 389
  Quarter4 443
Provider 2 1/4 chemo kpi
  Quarter1 385
  Quarter2 390
  Quarter3 377
  Quarter4 548
Provider 3 4/4 chemo kpi
  Quarter1 626
  Quarter2 408
  Quarter3 433
  Quarter4 407
Provider 4 0/4 kpi
  Quarter1 362
  Quarter2 318
  Quarter3 220
  Quarter4 270
Provider 5 2/4 chemo kpi
  Quarter1 226
  Quarter2 215
  Quarter3 472
  Quarter4 507
Provider 6 (leaves 2022) 1/3 chemo kpi
  Quarter1 447
  Quarter2 369
  Quarter3 274
  Quarter4 0
Provider 7 (leaves late 2021) 2/2.5 chemo kpi
  Quarter1 521
  Quarter2 529
  Quarter3 78
  Quarter4 0
Provider 8 0/4 chemo kpi
  Quarter1 239
  Quarter2 282
  Quarter3 213
  Quarter4 180

##unique patients seen 

```{r}
#make data frame that includes only each patient once and shows their diagnosis
unique <- data %>%
  group_by(Unique.Patient.ID) %>%
  distinct(Unique.Patient.ID, .keep_all = TRUE)
table(unique$Patient.Diagnosis)
table(unique$Provider.Name)
#cancer only data
unique1 <- unique %>%
  filter(Patient.Diagnosis == "Cancer")
table(unique1$Provider.Name)
#non-cancer only data
unique2 <- unique %>%
  filter(Patient.Diagnosis == "Non-Cancer")
table(unique2$Provider.Name)

#this lets me graph the data for some reason
unique1 <- unique1 %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))
#this code reorganizes the dates 
unique1$Quarter.of.Service <- factor(unique1$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

#graph of number of unique patients with cancer based on quarter
ggplot(unique1, aes(x = Quarter.of.Service, y = Quarter.of.Service1, fill = Quarter.of.Service)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  xlab("Quarter of Service") +
  ylab("Unique Patients with Cancer") +
  ggtitle("Number of Unique Patients with Cancer over 4 Quarters") +
  scale_fill_manual(values = c("lightcoral", "lightseagreen", "skyblue2", "thistle3")) +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()
  



```


//NEW PATIENTS
```{r}
newpat <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office")

newpat1 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 1")

newpat2 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 2")

newpat3 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 3")

newpat4 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 4")

newpat5 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 5")

newpat6 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 6")

newpat7 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 7")

newpat8 <- data %>%
  filter(Service.Subtype == "New Patient Visits - Office") %>%
  filter(Provider.Name == "Provider 8")

newpat1$Quarter.of.Service <- factor(newpat1$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat2$Quarter.of.Service <- factor(newpat2$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat3$Quarter.of.Service <- factor(newpat3$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat4$Quarter.of.Service <- factor(newpat4$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat5$Quarter.of.Service <- factor(newpat5$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat6$Quarter.of.Service <- factor(newpat6$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat7$Quarter.of.Service <- factor(newpat7$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))
newpat8$Quarter.of.Service <- factor(newpat8$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

table(newpat1$Quarter.of.Service, newpat1$Patient.Diagnosis)   
table(newpat2$Quarter.of.Service, newpat2$Patient.Diagnosis)
table(newpat3$Quarter.of.Service, newpat3$Patient.Diagnosis)
table(newpat4$Quarter.of.Service, newpat4$Patient.Diagnosis)
table(newpat5$Quarter.of.Service, newpat5$Patient.Diagnosis)
table(newpat6$Quarter.of.Service, newpat6$Patient.Diagnosis)
table(newpat7$Quarter.of.Service, newpat7$Patient.Diagnosis)
table(newpat8$Quarter.of.Service, newpat8$Patient.Diagnosis)

table(newpat1$Patient.Diagnosis)
table(newpat2$Patient.Diagnosis)
table(newpat3$Patient.Diagnosis)
table(newpat4$Patient.Diagnosis)
table(newpat5$Patient.Diagnosis)
table(newpat6$Patient.Diagnosis)
table(newpat7$Patient.Diagnosis)
table(newpat8$Patient.Diagnosis)


#this lets me graph the data for some reason
newpat <- newpat %>%
   mutate(Quarter.of.Service1 = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                          ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))
#this code reorganizes the dates 
newpat$Quarter.of.Service <- factor(newpat$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

#graph of number of new patients based on quarter
ggplot(newpat, aes(x = Quarter.of.Service, y = Quarter.of.Service1, fill = Quarter.of.Service)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  xlab("Quarter of Service") +
  ylab("New Patients") +
  ggtitle("Number of New Patients to all Providers over 4 Quarters") +
  scale_fill_manual(values = c("lightcoral", "lightseagreen", "skyblue2", "thistle3")) +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()


```


TARGET: 80 new patients per quarter per location

Provider 1 (new provider) kpi hit 2/4  53.4%
  Quarter1 88 (45 c)
  Quarter2 80 (40 c)
  Quarter3 45 (26 c)
  Quarter4 68 (39 c)
Provider 2 kpi hit 3/4 54%
  Quarter1 75 (43 c)
  Quarter2 86 (50 c)
  Quarter3 109 (51 c)
  Quarter4 82 (46 c)
Provider 3 kpi hit 2/4  58.7%
  Quarter1 91 (56 c)
  Quarter2 75 (44 c)
  Quarter3 90 (48 c)
  Quarter4 76 (47 c)
Provider 4 kpi hit 1/4  58.2%
  Quarter1 90 (50 c)
  Quarter2 73 (36 c)
  Quarter3 48 (34 c)
  Quarter4 45 (29 c)
Provider 5 kpi hit 4/4  39.2%
  Quarter1 172 (58 c)
  Quarter2 126 (51 c)
  Quarter3 194 (76 c)
  Quarter4 161 (71 c)
Provider 6 (leaves 2022) kpi hit 2/3  58.7%
  Quarter1 81 (52 c)
  Quarter2 74 (36 c)
  Quarter3 24 (17 c)
  Quarter4 0 (0)
Provider 7 (leaves late 2021) kpi hit 2/2  67%
  Quarter1 111 (71 c)
  Quarter2 101 (71 c)
  Quarter3 0 (0)
  Quarter4 0 (0)
Provider 8 kpi hit 1/4  31.8%
  Quarter1 77 (22 c)
  Quarter2 84 (31 c)
  Quarter3 56 (13 c)
  Quarter4 63 (23 c)



##PAYER MIX

```{r}
table(data$Payer, data$Provider.Name)

#this one used for kpi table
table(unique$Payer, unique$Provider.Name)

unique <- unique %>%
   mutate(Payer1 = ifelse(Payer == "Commercial", 1,
                                            ifelse(Payer == "Medicaid", 1,
                                                   ifelse(Payer == "Medicare", 1, 0))))

#make graph for unique patients of each type
ggplot(unique, aes(x = Provider.Name, y = Payer1)) +
  geom_bar(stat = "identity", aes(fill = Payer))


data <- data %>%
   mutate(Payer1 = ifelse(Payer == "Commercial", 1,
                                            ifelse(Payer == "Medicaid", 1,
                                                   ifelse(Payer == "Medicare", 1, 0))))
#graph of total pateints for each insurance
ggplot(data, aes(x = Provider.Name, y = Payer1)) +
  geom_bar(stat = "identity", aes(fill = Payer)) +
  xlab("") +
  ylab("Type of Insurance") +
  ggtitle("Trend in Insurance Type across all Providers") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()



```

##HOW IS NEW ONOCOLOSIGT (PROVIDER 1) DOING

```{r}
#dataframe filtered to new provider
onc1 <- data %>%
  filter(Provider.Name == "Provider 1")
#regex to allow us to make the payment amount column numerical
onc1$Payment.Amount <- gsub('\\$', '', onc1$Payment.Amount)

onc1$Payment.Amount <- gsub('\\(', '', onc1$Payment.Amount)

onc1$Payment.Amount <- gsub('\\)', '', onc1$Payment.Amount)

onc1$Payment.Amount <- gsub('\\.00', '.', onc1$Payment.Amount)

onc1$Payment.Amount <- substring(onc1$Payment.Amount, 1, nchar(onc1$Payment.Amount)-1)
onc1$Payment.Amount <- substring(onc1$Payment.Amount, 1, nchar(onc1$Payment.Amount)-1)

unique(onc1$Payment.Amount )

onc1 <- onc1 %>%
  mutate(Payment.Amount = as.numeric(Payment.Amount))

class(onc1$Payment.Amount)

unique(onc1$Payment.Amount)
#sorts the payment amount but not needed?
#str_sort(unique(onc1$Payment.Amount, numeric = TRUE))

#shows the sum of all the payments based on the quarter
aggregate(Payment.Amount ~ Quarter.of.Service, onc1, sum)
#lets us graph the values found in our aggregate
onc1 <- onc1 %>%
   mutate(test = ifelse(Quarter.of.Service == "1/1/2022", 603991.5,
                                            ifelse(Quarter.of.Service == "10/1/2021", 516607,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 372528,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 362891.5, 0)))))
#reorders dates correctly
onc1$Quarter.of.Service <- factor(onc1$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))


#graph showing the amount of payments to provider 1
ggplot(onc1, aes(x = Quarter.of.Service, y = test, fill = Provider.Name, group = Provider.Name)) +
  geom_point(show.legend = FALSE) +
  geom_line(color = 'indianred3') +
  xlab("Quarter of Service") +
  ylab("Payment Amount") +
  ggtitle("Trends in Payment Earned for Provider 1 per Quarter") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()



#provider 1 new patient visits
onc1new <- onc1 %>%
  filter(Service.Subtype == "New Patient Visits - Office")

table(onc1new$Service.Subtype, onc1new$Quarter.of.Service)

onc1new <- onc1new %>%
   mutate(Service.Subtype1 = ifelse(Quarter.of.Service == "1/1/2022", 68,
                                            ifelse(Quarter.of.Service == "10/1/2021", 45,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 88,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 80, 0)))))
#graph showing trned in new patients
ggplot(onc1new, aes(x = Quarter.of.Service, y = Service.Subtype1, fill = Service.Subtype, group = Service.Subtype)) +
  geom_point(show.legend = FALSE) +
  geom_line(color = 'cornflowerblue') +
  xlab("Quarter of Service") +
  ylab("Number of New Patients") +
  ggtitle("Number of New Patients to Provider 1 over 4 Quarters") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()




```

##changes to patient volume from provider 6 and 7 leaving near end of 2021

```{r}
data$Quarter.of.Service <- factor(data$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

ggplot(data, aes(x = Quarter.of.Service, y = final, fill = Quarter.of.Service)) +
  geom_bar(stat='identity', show.legend = FALSE) +
  xlab("Quarter of Service") +
  ylab("Total Services") +
  ggtitle("Total Amount of all Services done across all Providers over 4 Quarters") +
  scale_fill_manual(values = c("lightcoral", "lightseagreen", "skyblue2", "thistle3")) +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata() +
  scale_y_continuous(labels = comma)


table(data$Service.Type, data$Quarter.of.Service)

data <- data %>%
mutate(final = ifelse(Quarter.of.Service == "1/1/2022", 1,
                                            ifelse(Quarter.of.Service == "10/1/2021", 1,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 1,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 1, 0)))))
```


```{r}
leave671 <- data %>%
  filter(Service.Type == "Office Visit")

table(leave671$Quarter.of.Service)

leave671 <- leave671 %>%
   mutate(Service.Type1 = ifelse(Quarter.of.Service == "1/1/2022", 6003,
                                            ifelse(Quarter.of.Service == "10/1/2021", 6137,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 7230,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 7049, 0)))))

leave671$Quarter.of.Service <- factor(leave671$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

ggplot(leave671, aes(x=Quarter.of.Service, y=Service.Type1)) +
  geom_point()

ggplot(data, aes(x = Quarter.of.Service, y = Service.Type)) +
  geom_bar(stat='identity')
```

```{r}
leave672 <- data %>%
  filter(Service.Type == "Laboratory and Pathology")

table(leave672$Quarter.of.Service)

leave672 <- leave672 %>%
   mutate(Service.Type1 = ifelse(Quarter.of.Service == "1/1/2022", 619,
                                            ifelse(Quarter.of.Service == "10/1/2021", 559,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 716,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 648, 0)))))

leave672$Quarter.of.Service <- factor(leave672$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

ggplot(leave672, aes(x=Quarter.of.Service, y=Service.Type1)) +
  geom_point()
```

```{r}
leave673 <- data %>%
  filter(Service.Type == "Drug Administrations")

table(leave673$Quarter.of.Service)

leave673 <- leave673 %>%
   mutate(Service.Type1 = ifelse(Quarter.of.Service == "1/1/2022", 4292,
                                            ifelse(Quarter.of.Service == "10/1/2021", 4431,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 5406,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 4899, 0)))))

leave673$Quarter.of.Service <- factor(leave673$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

ggplot(leave673, aes(x=Quarter.of.Service, y=Service.Type1)) +
  geom_point()	

```


```{r}
table(data$Service.Type, data$Provider.Name, data$Quarter.of.Service)

  data <- data %>%
     mutate(PatientVolume = ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "4/1/2021", 1233,
                             ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "7/1/2021", 1205,
                             ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "10/1/2021", 1872,
                             ifelse(Provider.Name == "Provider 1" & Quarter.of.Service == "1/1/2022", 2207,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "4/1/2021", 1658,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "7/1/2021", 1781,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "10/1/2021", 1885,
                              ifelse(Provider.Name == "Provider 2" & Quarter.of.Service == "1/1/2022", 2699,                  
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "4/1/2021", 2002,
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "7/1/2021", 1337,
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "10/1/2021", 1494,
                                ifelse(Provider.Name == "Provider 3" & Quarter.of.Service == "1/1/2022", 1491,      
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "4/1/2021", 1274,
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "7/1/2021", 1173,
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "10/1/2021", 1033,
                                  ifelse(Provider.Name == "Provider 4" & Quarter.of.Service == "1/1/2022", 1092,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "4/1/2021", 1152,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "7/1/2021", 1037,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "10/1/2021", 1995,
                                    ifelse(Provider.Name == "Provider 5" & Quarter.of.Service == "1/1/2022", 2186,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "4/1/2021", 1723,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "7/1/2021", 1531,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "10/1/2021", 1149,
                                      ifelse(Provider.Name == "Provider 6" & Quarter.of.Service == "1/1/2022", 0,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "4/1/2021", 2955,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "7/1/2021", 3066,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "10/1/2021", 450,
                                        ifelse(Provider.Name == "Provider 7" & Quarter.of.Service == "1/1/2022", 0,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "4/1/2021", 1355,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "7/1/2021", 1466,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "10/1/2021", 1249,
                                          ifelse(Provider.Name == "Provider 8" & Quarter.of.Service == "1/1/2022", 1239, 0)))))))))))))))))))))))))))))))))

data$Quarter.of.Service <- factor(data$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))                                     
                                     
                                  
#graph showing the change in patient volume per provider through the quarters
ggplot(data, aes(x = Quarter.of.Service, y = PatientVolume, color = Provider.Name, group = Provider.Name)) +
  geom_point() +
  geom_line() +
  xlab("Quarter of Service") +
  ylab("Total Patient Volume") +
  ggtitle("Patient Volume Trend per all Providers across 4 Quarters") +
  scale_color_brewer(palette = "Dark2", name = "") +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata()



```



##trends in overall patient voulme and payment

```{r}

table(data$Service.Type, data$Quarter.of.Service)

data <- data %>%
   mutate(Service.Type11 = ifelse(Quarter.of.Service == "1/1/2022", 10914,
                                            ifelse(Quarter.of.Service == "10/1/2021", 11127,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 13352,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 12596, 0)))))

data$Quarter.of.Service <- factor(data$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

#graph of overall clinic visits 
ggplot(data, aes(x = Quarter.of.Service, y = Service.Type11, fill = Service.Type, group = Service.Type)) +
  geom_point(show.legend = FALSE) +
  geom_line(color = 'mediumpurple2') +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata() +
  xlab("Quarter of Service") +
  ylab("Overall Patient Volume") +
  ggtitle("Trends in Overall Patient Volume across all Providers")


```


```{r}
#dataframe filtered to new provider
money <- data
 
#regex to allow us to make the payment amount column numerical
money$Payment.Amount <- gsub('\\$', '', money$Payment.Amount)

money$Payment.Amount <- gsub('\\(', '', money$Payment.Amount)

money$Payment.Amount <- gsub('\\)', '', money$Payment.Amount)

money$Payment.Amount <- gsub('\\.00', '.', money$Payment.Amount)

money$Payment.Amount <- substring(money$Payment.Amount, 1, nchar(money$Payment.Amount)-1)
money$Payment.Amount <- substring(money$Payment.Amount, 1, nchar(money$Payment.Amount)-1)

unique(money$Payment.Amount )

money <- money %>%
  mutate(Payment.Amount = as.numeric(Payment.Amount))

class(money$Payment.Amount)

unique(money$Payment.Amount)

#shows the sum of all the payments based on the quarter
aggregate(Payment.Amount ~ Quarter.of.Service, money, sum)
#lets us graph the values found in our aggregate
money <- money %>%
   mutate(test = ifelse(Quarter.of.Service == "1/1/2022", 3306360,
                                            ifelse(Quarter.of.Service == "10/1/2021", 3358102,
                                                   ifelse(Quarter.of.Service == "4/1/2021", 4040660,
                                                      ifelse(Quarter.of.Service == "7/1/2021", 3814279, 0)))))
#reorders dates correctly
money$Quarter.of.Service <- factor(money$Quarter.of.Service, levels = c("4/1/2021", "7/1/2021", "10/1/2021", "1/1/2022"))

#graph showing overalltrend in payments
ggplot(money, aes(x = Quarter.of.Service, y = test, fill = Service.Type, group = Service.Type)) +
  geom_point(show.legend = FALSE) +
  geom_line(color = 'violetred2') +
  theme(plot.title = element_text(hjust = 0.4)) +
  theme_stata() +
  xlab("Quarter of Service") +
  ylab("Overall Payment Recieved") +
  ggtitle("Trends in Overall Payment Recieved across all Providers")


```